CorReg pretreatment : Regression for correlated variables and application in steel industry

### 2014-03-14 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@452 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

We can now write the generative model:
\begin{itemize}
	\item Main regression between $Y$ and $X$:
		\begin{equation}
			Y_{|S}=XA+\varepsilon_Y =X_1A_1+X_2A_2+\varepsilon_Y \textrm{ whith } \varepsilon_Y \sim \mathcal{N}(0,\sigma^2_YI_n);	\label{MainR}
		\end{equation}
		where $A=(A_1,A_2) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $I_n$ the identity matrix, 
	\item Family of $p_2$ regressions within correlated covariates in $X$:
		\begin{equation}
			\forall j \in I_2: X^j_{|X_1,S}=X_1B^j_1+\varepsilon_j \textrm{ with } \varepsilon_j \sim(0,\sigma^2_jI_n); \label{SR}
		\end{equation}
		where $B_1^j \in \mathcal{R}^{(p-p_2)}$ are the vectors of the regression coefficients between the covariates (containing some zeros according to $I_1^j$).
	\item  $p-p_2$ remaining independent exogenous variables:
		\begin{equation}
			\forall j \notin I_2 : X^j_{|S} \sim f(\theta_j)%=\mathcal{GM}(\pi_j;\mu_j;\sigma^2_j) \textrm{ with } \pi_j,\mu_j,\sigma^2_j \textrm{ vectors of size } k_j; \label{mixtureX1v0}
		\end{equation}
\end{itemize}

@@

This generative model is conditionnal to $S$, the discrete structure model that is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(X,Y)$, the residuals ($\varepsilon_j$) would not stay Gaussian. These residuals are in the following supposed independent but one can suppose dependencies between them and then use appropriate tools to estimate them and the $B_1^j$ like SUR with Feasible Generalized Least Squares (FGLS) by Zellner \cite{SURzellner} or SPRING \cite{chiquetconf} as mentioned in the introduction.
\\
If there are exact regressions ($\sigma^2_j=0$) in (\ref{SR}), the structure won't be identifiable. But it only means that several structure will have the same likelihood and they will have the same interpretation. So it's not really a problem. Moreover, when an exact subregression is found, we can delete one of the implied variables without any loss of information and the structure will define a list of variable from which to delete. CorReg (Our R package) prints a warning to point out exact regressions when found.

@@

		At the opposite, methods like the LASSO with LAR will only keep one covariate for each group of correlated covariates  so we get $\hat{Y}=2aX_1$ and think that $X_2 \perp Y$ but $Y$ depends on $X_2$.

			Nothing constrains us to give only one equation. It is clearly better to give the user another equation (or system for more complex models) describing the correlations. 
			So you get the following model : $Y=aX_1+aX_2$ and $X_1=X_2+e$. Then you have more information and are able to decide better actions. 
			With such a model, grouping effect is no more useful because when saying $Y=2aX_1$ and $X_2=X_1+e$ with the information that $X_2$ has been removed locally because of its correlation with $X_1$, you don't get misleading interpretations anymore. In fact, we have two kinds of zeros (those from selection and those from correlations) and we know for each zero which kind is it.
			So it is possible to combine the advantages of grouping effect and selection just giving several equations. 
			Each equation here is very simple (only linear regressions) so you don't really increase complexity of the model. 
			Moreover, the uncrossing constraint ($I_1\cap I_2=\emptyset$) guarantee to keep a simple structure easily interpretable.

@@

\section{Numerical results on simulated datasets}
	\subsection{The datasets}	
	Now we have defined the model and the way to obtain it, we can have a look on some numerical results to see if \textsc{CorReg} 	keeps its promises.
	The \textsc{CorReg} package has been tested on simulated datasets. 
Section \ref{compZ} show the results obtained in terms of $\hat{S}$. Sections \ref{tableMSEsimtout} et \ref{tableMSEsimgauche} show the results obtained using only \textsc{CorReg}, or \textsc{CorReg} combined with other methods. Tables give both mean and standard deviation of the observed Mean Squared Errors (MSE) on a validation sample of $1 000$ individuals. For each simulation ,  $p=40$, $\sigma_Y=10$, $\sigma=0.001$, variables $X_1$ follow Gaussian mixture models of $\lambda=5$ classes which means follow Poisson's law of parameter $\lambda$ and which standard deviation also is $\lambda$. The $B_1^j$ are generated according to the same Poisson law but with a random sign. $S$ only contains binary relationships but \textsc{CorReg} was only constrained to $\max (\hat{p}_1^j)=5$.  
	We used \textsc{Rmixmod} to estimate the densities of each covariate.

>>>>

We can now write the generative model:
\begin{itemize}
	\item Main regression between $Y$ and $X$:
		\begin{equation}
			Y_{|S}=XA+\varepsilon_Y =X_1A_1+X_2A_2+\varepsilon_Y \textrm{ whith } \varepsilon_Y \sim \mathcal{N}(0,\sigma^2_YI_n);	\label{MainR}
		\end{equation}
		where $A=(A_1,A_2) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $I_n$ the identity matrix, 
	\item Family of $p_2$ regressions within correlated covariates in $X$:
		\begin{equation}
			\forall j \in I_2: X^j_{|X_1,S}=X_1B^j_1+\varepsilon_j \textrm{ with } \varepsilon_j \sim(0,\sigma^2_jI_n); \label{SR}
		\end{equation}
		where $B_1^j \in \mathcal{R}^{(p-p_2)}$ are the vectors of the regression coefficients between the covariates (containing some zeros according to $I_1^j$).
\end{itemize}
It remains $p-p_2$ independent exogenous variables : $\forall j \notin I_2 : X^j_{|S} \sim f(\theta_j)$

@@

This generative model is conditional to $S$, the discrete structure model that is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(X,Y)$, the residuals ($\varepsilon_j$) would not stay Gaussian. These residuals are in the following supposed independent but one can suppose dependencies between them and then use appropriate tools to estimate them and the $B_1^j$ like SUR with Feasible Generalized Least Squares (FGLS) by Zellner \cite{SURzellner} or SPRING \cite{chiquetconf} as mentioned in the introduction.
\\
If there are exact regressions ($\sigma^2_j=0$) in (\ref{SR}), the structure won't be identifiable. But it only means that several structure will have the same likelihood and they will have the same interpretation. So it's not really a problem. Moreover, when an exact sub-regression is found, we can delete one of the implied variables without any loss of information and the structure will define a list of variable from which to delete. \textsc{CorReg} (Our R package) prints a warning to point out exact regressions when found.

@@

		At the opposite, methods like the LASSO with LAR will only keep one covariate for each group of correlated covariates  so we get $\hat{Y}=2aX_1$ and think that $X_2 \perp Y$ but $Y$ depends on $X_2$ so it is worse than grouping effect for interpretation.

			Nothing constrains us to give only one equation. It is clearly better to give the user another equation (or system for more complex models) describing the correlations. 
			So you get the following model : $Y=aX_1+aX_2$ and $X_1=X_2+e$. Then you have more information and are able to decide better actions. 
			With such a model, grouping effect is no more useful because when saying $Y=2aX_1$ and $X_2=X_1+e$ with the information that $X_2$ has been removed locally because of its correlation with $X_1$, you don't get misleading interpretations anymore. In fact, we have two kinds of zeros (those from selection and those from correlations) and we know for each zero which kind is it.
			So it is possible to combine the advantages of grouping effect and selection just giving several equations. 
			Each equation here is very simple (only linear regressions) so you don't really increase complexity of the model. 
			Moreover, the uncrossing constraint ($I_1\cap I_2=\emptyset$) guarantee to keep a simple structure easily interpretable (no cycles and no chain-effect).

@@

\section{Numerical results on simulated datasets}
	\subsection{The datasets}	
	Now we have defined the model and the way to obtain it, we can have a look on some numerical results to see if \textsc{CorReg} 	keeps its promises.
	The \textsc{CorReg} package has been tested on simulated datasets. 
Section \ref{compZ} show the results obtained in terms of $\hat{S}$. Sections \ref{tableMSEsimtout} et \ref{tableMSEsimgauche} show the results obtained using only \textsc{CorReg}, or \textsc{CorReg} combined with other methods. Tables give both mean and standard deviation of the observed Mean Squared Errors (MSE) on a validation sample of $1 000$ individuals. For each simulation ,  $p=40$, $\sigma_Y=10$, $\sigma=0.001$, variables $X_1$ follow Gaussian mixture models of $\lambda=5$ classes which means follow Poisson's law of parameter $\lambda$ and which standard deviation also is $\lambda$. The $B_1^j$ are generated according to the same Poisson law but with a random sign. $S$ only contains binary relationships but \textsc{CorReg} was only constrained to $\max (\hat{p}_1^j)=5$.  
	We used \textsc{Rmixmod} to estimate the densities of each covariate. For each configuration, the walk was launched on $20$ initial structures with a maximum of 9 000 steps each time.
